A Pitman-Yor process prior for estimating shared evolutionary events

### 2021-03-02 manuscript/ms.tex
Adding bib files in ms directory.
Overleaf cannot seem to handle the bib/bst files being in a different
directory from the main tex file, so adding copies to the manuscript
directory. Not cool at all.
Working on incorporating new plots into ms.
Also, adding references.

@@

\bibliographystyle{../bib/evolution}
\bibliography{../bib/references}

>>>>

We found that the DP, PYP, and WU models estimated the number of divergence
events (\nevents) similarly well when applied to \datasets simulated under one
of the these models (\fig~\ref{fig:neventsgrid}).
However, when we compare the ability of the models to estimate
the divergence model (\etimesets), we see that the WU
model underperforms relative to the DP and PYP models when applied
to data generated under the DP and PYP models
(first two rows of \fig~\ref{fig:modeldistancegrid}).
The DP and PYP models show more robustness when applied to
data generated under the WU model
(bottom row of \fig~\ref{fig:modeldistancegrid}).

When applied to \datasets where all 10 pairs of populations diverged
independently, the PYP model performs slightly better than the other two models
(top row of \fig~\ref{fig:neventsfixedcomparison}).
All three models almost always correctly infer a single shared divergence event
with high posterior probability when it is true
(bottom row of \fig~\ref{fig:neventsfixedcomparison}).

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/model-performance-violin-cropped.pdf}
        \captionsetup{listformat=figList}
        \caption{
        Comparing the models' ability to estimate the divergence model.
        Each column of plots compares the performance of the Dirichlet process
        (DP), Pitman-Yor process (PYP) and weighted-uniform (WU) models when
        analyzing 720 \datasets simulated under the (from left-to-right)
        simultaneous-divergence, DP, PYP, WU, and independent-divergences
        model. 
        The first row shows the mean distance from the true
        divergence model (\etimesets) of the posterior samples
        \citep{Kuhn1955,Munkres1957,Gusfield2002} calculated
        using Version 1.1.4 of the munkres Python package
        \citep{Clapper2020}.
        We generated the plot using matplotlib Version 3.1.3
        \citep{matplotlib}.
        }
        \label{fig:modeldistancegrid}
    \end{center}
\end{figure}

@@

\bibliographystyle{evolution}
\bibliography{references}
